Evaluate PEER in each cohort and brain region

### 2020-11-23 combined_analysis/eval_resid_in_each.Rmd
add CTS

>>>>

# Cell Type Specific expression from bMIND

```{r}
# create new parent folder for these results
CODE <- Folder(name = "CTS - Evaluate PEER in each cohort and brain region", parentId = "syn23567522")
CODE <- synStore(CODE)

```{r CTS.download}
geneExpr.CTS = readRDS( synGet('syn23234833')$path )

# formula used to fit model
form.lst = list(
  `MSSM-Penn-Pitt`  = ~ Dx + Reported_Gender + RIN +scale(IntronicRate) + scale(IntragenicRate) + scale(IntergenicRate) + scale(rRNARate) + Institution*ageOfDeath,
  `NIMH-HBCC`       = ~ Dx + Reported_Gender + RIN + scale(IntronicRate) + scale(IntragenicRate) + scale(IntergenicRate) + scale(rRNARate) + ageOfDeath)

# for each dataset
for( datID in names(dge.lst) ){

  # get formula
  j = unlist(sapply(names(form.lst), function(x) grep(x, datID)))
  form_use = form.lst[[names(j)]]

  # extract CTS data corresponding to info
  idx = match(info$SampleID, dimnames(geneExpr.CTS)[[3]])
  geneExpr = geneExpr.CTS[,,idx]

  # identical(dimnames(geneExpr)[[3]], info$SampleID)

  # for each cell type
  for( i in length(dimnames(geneExpr)[[2]]) ){

    PEER_setPhenoMean(model, t(geneExpr[1:100,i,]))

    PEER_setNk(model,2)

    # upload observed expression
    file = paste0('geneExpr_',gsub(" ", '', gsub("-", "_", datID)), ".RDS")
    storeData( vobj$E, file, paste0(datID, " Observed expression"))

    # upload latent variables
    file = paste0('PEER',gsub(" ", '', gsub("-", "_", datID)), ".RDS")
    storeData( latentVariables, file, paste0(datID, " Latent variables for QTL analysis"))
  }
}
```
